Region-network hierarchical sparsity priors for\\ high-dimensional inference in brain imaging

### 2016-01-26 paper/paper.tex
interm

\paragraph{Support recovery as a function of region and network emphasis.}
Finally, the relative importance of the
region and network priors within the hierarchical tree prior
was quantified (Figure \ref{fig_regnetratio}).
The $\eta_g$ group of region priors was multiplied with a
region-network ratio, while the
$\eta_g$ group of network priors was biased by the corresponding
network-region ratio. A region-network ratio of 3, for instance,
increased the relative importance of known region structure
by multiplying \frac{3}{1} to the
$\eta_g$ factor of all region groups
and multiplying
\frac{1}{3} to all network groups.
The data splitting cross-validation scheme was identical to the
above modelling experiments.
%
As the most important observation,
a range between region-dominant and network-dominant structured penalties
yields quantitatively almost identical generalization to new data
but qualitatively different decision functions manifested in the weight maps
(Figure \ref{fig_regnetratio}, 2. and 4. column).
Classification models with many zero coefficients but high absolute
coefficients in either region compartments or network compartments
can similarly extrapolation to unseen neural activity maps.
Second,
these perform similar to equilibrated region-network priors
that set less voxel coefficients to zero and spread the
probability mass with lower absolute coefficients across the whole brain
(Figure \ref{fig_regnetratix}, 3. column in the middle).
Third,
overly strong emphasis on either level of the hierarchical prior
can yield the neurobiologically informative maps
of the most necessary region or network structure for
statistically significant out-of-sample performance
(Figure \ref{fig_regnetratix}, leftmost and rightmost columns).
%
In sum,
stratifying the hierarchical tree penalty between region and network emphasis
suggests that \textit{class-specific region-network weights}
might offer more performant and more interpretable classification models
in the future.

>>>>

\paragraph{Support recovery as a function of region and network emphasis.}
Finally, the relative importance of the
region and network priors within the hierarchical tree prior
was quantified (Figure \ref{fig_regnetratio}).
The $\eta_g$ group of region priors was multiplied with a
region-network ratio, while the
$\eta_g$ group of network priors was biased by the corresponding
network-region ratio. A region-network ratio of 3, for instance,
increased the relative importance of known region structure
by multiplying $\frac{3}{1}$ to the
$\eta_g$ factor of all region groups
and multiplying
$\frac{1}{3}$ to all network groups.
The data splitting cross-validation scheme was identical to the
above modelling experiments.
%
As the most important observation,
a range between region-dominant and network-dominant structured penalties
yields quantitatively almost identical generalization to new data
but qualitatively different decision functions manifested in the weight maps
(Figure \ref{fig_regnetratio}, second and forth column).
Classification models with many zero coefficients but high absolute
coefficients in either region compartments or network compartments
can similarly extrapolation to unseen neural activity maps.
Second,
these perform similar to equilibrated region-network priors
that set less voxel coefficients to zero and spread the
probability mass with lower absolute coefficients across the whole brain
(Figure \ref{fig_regnetratio}, third column in the middle).
Third,
overly strong emphasis on either level of the hierarchical prior
can yield the neurobiologically informative maps
of the most necessary region or network structure for
statistically significant out-of-sample performance
(Figure \ref{fig_regnetratio}, leftmost and rightmost columns).
%
In sum,
stratifying the hierarchical tree penalty between region and network emphasis
suggests that \textit{class-specific region-network weights}
might offer more performant and more interpretable classification models
in the future.
